---
title: "SRIvidhya: End-to-End Synthetic Stratum Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SRIvidhya: End-to-End Synthetic Stratum Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Purpose

This vignette walks through the SRIvidhya v0.1 workflow end to end using a
**synthetic** stratum. All numbers in this document are illustrative
placeholders, explicitly tagged `evidence_tier = "provisional_default"`.
They are not agronomic recommendations and must never be substituted for
local measurement or calibration.

```{r setup}
library(srividhya)
```

## 1. Define a project stratum

A stratum groups fields sharing cultivar, establishment method, soil
profile, irrigation setting, and materially relevant management conditions.

```{r}
stratum <- srividhya_define_stratum(
  stratum_id = "SYNTHETIC_A",
  cultivar = "Synthetic cultivar (example only)",
  establishment_method = "transplanted",
  soil_profile_id = "SYNTHETIC_PROFILE_CLAY",
  irrigation_setting = "controlled irrigation",
  management_notes = "Synthetic example; not calibration data.",
  root_parameters = list(
    R_max_cm = 30, R0_cm = 3, k_day_inv = 0.12,
    evidence_tier = "provisional_default",
    evidence_source = "Synthetic demonstration only"
  ),
  percolation_parameters = list(
    P_cm_h = 0.18,
    evidence_tier = "provisional_default",
    evidence_source = "Synthetic demonstration only"
  ),
  safety_parameters = list(
    alpha = 0.50, D_max_cm = 12, psi_threshold_kpa = -20,
    verification_rule = "either",
    evidence_tier = "provisional_default"
  ),
  soc_parameters = list(
    SOC_g_kg = 10, f_low_events_season = 3, f_high_events_season = 4,
    evidence_tier = "provisional_default"
  )
)
stratum
```

Note that every parameter group reports `provisional_default`. This is by
design: SRIvidhya never assumes empirical defaults for `R_max`, `k`, `t50`,
`alpha`, `D_max`, `psi_threshold`, `f_low`, or `f_high`.

## 2. Root-depth trajectory and safe drainage ceiling

```{r}
dat_seq <- seq(0, 60, by = 5)
root_depth <- srividhya_root_depth(
  dat = dat_seq, R_max_cm = stratum$root_parameters$R_max_cm,
  k_day_inv = stratum$root_parameters$k_day_inv,
  R0_cm = stratum$root_parameters$R0_cm
)
safe_depth <- srividhya_safe_depth(
  root_depth, alpha = stratum$safety_parameters$alpha,
  D_max_cm = stratum$safety_parameters$D_max_cm
)
data.frame(DAT = dat_seq, root_depth_cm = round(root_depth, 1),
           safe_depth_ceiling_cm = round(safe_depth, 1))
```

Early in the season, the root-safety constraint (`alpha * R(t)`) is more
restrictive than the agronomic ceiling (`D_max_cm`); later, once roots are
established, the ceiling itself becomes the binding constraint.

## 3. Time to reach the safe depth

```{r}
srividhya_time_to_target(target_depth_cm = safe_depth,
                          P_cm_h = stratum$percolation_parameters$P_cm_h,
                          units = "hours")
```

## 4. SOC-scaled seasonal drainage frequency

```{r}
srividhya_soc_frequency(
  SOC_g_kg = stratum$soc_parameters$SOC_g_kg,
  f_low_events_season = stratum$soc_parameters$f_low_events_season,
  f_high_events_season = stratum$soc_parameters$f_high_events_season
)
```

## 5. Generate the full calendar

```{r}
calendar <- srividhya_generate_calendar(stratum, dat_seq = c(5, 20, 35, 50))
calendar[, c("DAT", "root_depth_cm", "safe_depth_ceiling_cm",
             "expected_time_to_target_hours", "verification_status",
             "data_quality_flag")]
```

## 6. Farmer-facing instruction

```{r}
cat(srividhya_farmer_instruction(calendar[3, ]))
```

## What this vignette does not show

This vignette does not fit `k` or `t50` from repeated root observations, does
not fit a depth-dependent percolation curve from field data, and does not
propagate parameter uncertainty via Monte Carlo simulation. Those
capabilities are planned for subsequent SRIvidhya milestones and will
operate on the same `srividhya_stratum` object shown here.
